---
title: "R Notebook"
output: latex_fragment
---

The [R plugin](https://www.jetbrains.com/help/pycharm/r-plugin-support.html) for IntelliJ-based IDEs provides
handy capabilities to work with the [R Markdown](https://www.jetbrains.com/help/pycharm/r-markdown.html) files.
To [add](https://www.jetbrains.com/help/pycharm/r-markdown.html#add-code-chunk) a new R chunk,
```{r}
# Lewis Higgins, Student ID 22133848
# Code for CMP5352 Data Visualisation Quiz 1

# Necessary for diamonds and mpg dataset, and the graph plotting.
library(ggplot2)

# Question 1
# First graph shows the relation of carats and price by color.

qplot(log(carat), log(price), data = diamonds, color = color, geom = c("point", "smooth"))

# Second graph shows the relation of carats and price by cut.

qplot(log(carat), log(price), data = diamonds, color = cut, geom = c("point", "smooth"))


# Question 2
# Produces 4 plots, one for each amount of cylinders.

qplot(displ, hwy, data = mpg, facets = cyl ~ ., color = factor(cyl), geom = c("point", "smooth"))

# Question 3
# Colors by cylinder, and adds smootihng lines for each color.

qplot(displ, hwy, data = mpg, color = factor(cyl), geom = c("point", "smooth"))

# For the exact numbers for the hwy values.
# View(mpg)


```
position the caret at any line or the code chunk, then click "+".

The code chunk appears:
```{r}
```

Type any R code in the chunk, for example:
```{r}
mycars <- within(mtcars, { cyl <- ordered(cyl) })
mycars
```

Now, click the **Run** button on the chunk toolbar to [execute](https://www.jetbrains.com/help/pycharm/r-markdown.html#run-r-code) the chunk code. The result should be placed under the chunk.
Click the **Knit and Open Document** to build and preview an output.